---
title: "Untitled"
author: "Lorenz Walthert"
date: "5/19/2018"
output: html_document
---

```{r}
knitr::opts_knit$set(cache = TRUE)
library(tidyverse)
raw <- read_tsv(here::here("competition/01-data/train.csv"))
if (!("answer_score" %in% names(raw))) {
  raw$answer_score <- NA
}
train <- raw
head <- train %>% head()
```


# Pre-processing

```{r}
library(lubridate)
dt_from_unix <- function(vec) {
  as.POSIXct(vec, origin = "1970-01-01")
}


remove_cols <- function(data) {
  data %>%
    select(-.data$question_utc, -.data$answer_utc)
}

transform_response <- function(data) {
  data %>%
    mutate(
      log_answer_score = log(answer_score), 
      log10_answer_score = log10(answer_score) 
    )
}
convert_time <- function(data) {
    data %>%
    mutate(
      question_dt = dt_from_unix(question_utc),
      answer_dt = dt_from_unix(answer_utc)
    ) %>%
    mutate(
      question_day = day(question_dt),
      answer_day = day(answer_dt),
      question_hour = hour(question_dt),
      answer_hour = hour(answer_dt),
      question_weekday = weekdays.Date(question_dt),
      answer_weekday = weekdays.Date(answer_dt)
    )
}

reorder_cols <- function(data) {
  question <- grep("question", names(data), value = TRUE)
  answer <- grep("answer", names(data), value = TRUE)
  important <- c("subreddit", "question_score", "answer_score")
  rest <- setdiff(names(data), c(question, answer, important))
  
  data[, unique(c(important, question, answer, rest))]
}

txt_from_stats <- function(data) {
  data %>%
    mutate(answer_nchar = nchar(answer_text))
}
  
time_to_answer <- function(data)  {
  data %>%
    mutate(time_to_answer = as.numeric(question_dt - answer_dt))

}

time_to_next_answer <- function(data) {
  data %>%
    group_by(question_id) %>%
    mutate(
      time_to_next_anser = lag(answer_dt, default = 0),
      time_to_previous_anser = lead(answer_dt, default = NA)
    ) %>%
    ungroup()
}

rank_in_answer <- function(data) {
  data %>%
    group_by(question_id) %>%
    mutate(nth_answer = 1:n()) %>%
    ungroup()
}


pre_process <- function(data) {
  data %>%
    convert_time() %>%
    arrange(question_dt, answer_dt) %>%
    transform_response() %>%
    txt_from_stats() %>%
    time_to_answer() %>% 
    time_to_next_answer() %>%
    rank_in_answer %>%
    reorder_cols() %>%
    remove_cols()
}
```

```{r}
temp <- head %>%
  pre_process()
```

Ok, it works :-). Lets pre-process the whole dataset.

```{r}
library(magrittr)
train %<>%
  pre_process()

fst::write_fst(train, here::here("competition/01-data/cleaned"))
```


# Exploratory Data Analysis

The data set contains `r nrow(train)` obeservations. That's not very comfortable
to work with. Let's sub-sample that an work with the reduced data set.

```{r}
small_train <- train %>%
  select(-contains("text")) %>%
  sample_frac(0.1)
```


Let's have a look at some descriptive plots. 

```{r}
small_train %>%
  ggplot(aes(x = answer_score)) +
  geom_histogram() + 
  scale_x_continuous(trans = "log10", breaks = c(1:5, 10, 100, 1000))
```

We've also created transformations of it:

```{r}
small_train %>%
  ggplot(aes(x = log_answer_score)) +
  geom_histogram()
```


```{r}
full <- small_train %>%
  ggplot(aes(x = question_score, y = answer_score)) + 
  geom_point() + 
  stat_smooth()
```

Most questions and answers arbe in the 10k / 10k space. Let's have a closer look

```{r}
ten_k <- small_train %>%
  filter(question_score < 10000, answer_score < 10000) %>%
  sample_frac(0.1) %>%
  ggplot(aes(x = question_score, y = answer_score)) + 
  geom_point() + 
  stat_smooth()

```

Also here, there seems not really a direct relationship between the variables.
```{r}
gridExtra::grid.arrange(full, ten_k)
```

Next, we check how date and time is related to upvotes.
```{r}
uncut <- small_train %>%
  ggplot(aes(x = factor(answer_weekday), y = answer_score)) + 
  geom_violin() + 
  scale_y_continuous(trans = "log10", name = "Answer Score") + 
  scale_x_discrete(name = "Weekday")

cut <- small_train %>%
  filter(answer_score <10) %>%
  ggplot(aes(x = factor(answer_weekday), y = answer_score)) + 
  geom_violin() + 
  scale_y_continuous(trans = "log10", name = "Answer Score") + 
  scale_x_discrete(name = "Weekday")
gridExtra::grid.arrange(uncut, cut)
```

Not much interesting here. Let's check whether time of answer matters. 

```{r}
small_train %>%
  ggplot(aes(x = answer_hour, y = log(answer_score))) + geom_jitter() + 
  scale_y_continuous(trans = "log10") + 
  geom_smooth()
```
```{r}
train %>%
  mutate(question_score_zero = (question_score == 1L)) %>%
  group_by(question_score_zero) %>%
  count()


train %>%
  mutate(question_score_one = (question_score == 1L)) %>%
  group_by(subreddit) %>%
  summarise(n = n(), is_one = mean(question_score_one)) %>%
  arrange(desc(is_one))
```

Feature engineering is key
